### 2019-09-16 papers/journal/2019_ACTA_Rebuttal_Rd2.txt

% Reviewer 1:
 > My comments and concerns have been addressed in detail. Thank you.

% Reviewer 3:

> I believe that most issues highlighted previously have been 
  addressed adequately. In particular, the structure of the 
  revised manuscript has been improved significantly. 
  I still found the paper challenging to read, but this is 
  largely due to the complexity of the biological system and 
  the necessary encoding details presented in the manuscript.

  Pt #1a:
-------- Handle by Mukund --------------
  One point that I think requires further attention is the 
  motivation for using connectedness and the explanation of 
  this property, which is at the core of the proposed approach. 
  I did not find the additional explanations provided in the 
  response and the revised manuscript sufficient. Simply stating 
  that "The graph k-connectedness furnishes precisely" a test to 
  determine if information is missing from the model and that 
  "If the data […] does not have a certain degree of connectivity, 
  this implies that some biological data has been missed" does not 
  justify connectedness as a fundamental and required biological 
  property that all valid models should respect. The intuition of 
  connectedness as a robustness property provided elsewhere in the 
  manuscript helps but it is still not clear what evidence supports 
  the fact that VTSs are indeed robust. In addition, the problem as 
  formulated does not seem to seek the most robust networks as 
  explained in the following.

  Pt #1b:
-------- Handle by Mukund [Subpoint added]--------------
    Finally, it is not clear why the goal is to find the minimum graph 
    connectivity, given that larger connectivity corresponds to a 
    more robust network. I was expecting an approach involving 
    incrementing k to find the smallest value that makes the formula 
    unsatisfiable, thus identifying the maximum graph connectedness 
    possible for a given VTS with all other constraints being 
    satisfied. However, to the best of my understanding, this is not 
    what the paper is currently proposing, or else further  
    clarifications are needed.

  > I also found the formulation of the main problems with respect 
    to connectedness somewhat confusing. For example, in Sec. 5.1.1 
    and Sec. 5.1.2 the problems are formulated as a search for VTS G 
    such that G is not k-connected. Yet, Sec. 5.1 specifies that 
    "In case the formula is satisfiable the procedure terminates and 
    we report the value of k", which seems contradictory.

  Authors response: In Sec. 5 we try to achieve two aims: give a 
  high-level explanation of the problem, followed by a formal search 
  statement (from a prespective of an efficient implementation). 
  This difference was only hinted but not explicitely stated. We have 
  now rewritten the parts of the text to address the distinction 
  between high-level overview and the implementation. 
  We have also removed the specific search problems (as suggested by 
  Reviewer #3 in the first revision) for further apparent accessibility 
  of the subject matter.

@@

  > There is overlap in the 3rd and 6th paragraphs of 
    the 'Related Work' section, which refer to the use 
    of SAT/SMT in GRNs.

  Authors response: The use of SAT/SMT in GRN is presented
  in two different context (non-overlapping references). 
  The third paragrah points to general use of SAT/SMT 
  solvers in GRN, whereas 6th paragraph refers to a specific
  use (synthesis). We have updated the text to improve this
  distinction.

Minor points:

  > Small typos / grammatical errors. There are a number 
    of these throughout the text, some of which are listed 
    below (this is not exhaustive, so I recommend carefully 
    reading the manuscript to ensure clarity):
  Authors response: We thank the reviewer for pointing these 
  out. We have corrected the listed errors and performed 
  careful readings fixing other errors that we found.

### 2019-09-16 papers/journal/2019_ACTA_Rebuttal_Rd2.txt

% Reviewer 1:
 > My comments and concerns have been addressed in detail. Thank you.

% Reviewer 3:

> I believe that most issues highlighted previously have been 
  addressed adequately. In particular, the structure of the 
  revised manuscript has been improved significantly. 
  I still found the paper challenging to read, but this is 
  largely due to the complexity of the biological system and 
  the necessary encoding details presented in the manuscript.

  Pt #1a:
-------- Mukund --------------
  > One point that I think requires further attention is the 
  motivation for using connectedness and the explanation of 
  this property, which is at the core of the proposed approach. 
  I did not find the additional explanations provided in the 
  response and the revised manuscript sufficient. Simply stating 
  that "The graph k-connectedness furnishes precisely" a test to 
  determine if information is missing from the model and that 
  "If the data […] does not have a certain degree of connectivity, 
  this implies that some biological data has been missed" does not 
  justify connectedness as a fundamental and required biological 
  property that all valid models should respect. The intuition of 
  connectedness as a robustness property provided elsewhere in the 
  manuscript helps but it is still not clear what evidence supports 
  the fact that VTSs are indeed robust. In addition, the problem as 
  formulated does not seem to seek the most robust networks as 
  explained in the following.

  Authors response: ...

  Pt #1b:
-------- Mukund [Subpoint added]--------------
  > Finally, it is not clear why the goal is to find the minimum graph 
    connectivity, given that larger connectivity corresponds to a 
    more robust network. I was expecting an approach involving 
    incrementing k to find the smallest value that makes the formula 
    unsatisfiable, thus identifying the maximum graph connectedness 
    possible for a given VTS with all other constraints being 
    satisfied. However, to the best of my understanding, this is not 
    what the paper is currently proposing, or else further  
    clarifications are needed.

  Authors response: ...

### 2019-09-16 papers/journal/2019_ACTA_Rebuttal_Rd2.txt

  Authors response: ...

  > I also found the formulation of the main problems with respect 
    to connectedness somewhat confusing. For example, in Sec. 5.1.1 
    and Sec. 5.1.2 the problems are formulated as a search for VTS G 
    such that G is not k-connected. Yet, Sec. 5.1 specifies that 
    "In case the formula is satisfiable the procedure terminates and 
    we report the value of k", which seems contradictory.

  Authors response: In Sec. 5 we try to achieve two aims: give a 
  high-level explanation of the problem, followed by a formal search 
  statement (from a prespective of an efficient implementation). 
  This difference was only hinted but not explicitely stated. We have 
  now rewritten the parts of the text to address the distinction 
  between high-level overview and the implementation. 
  We have also removed the specific search problems (as suggested by 
  Reviewer #3 in the first revision) for further apparent accessibility 
  of the subject matter.

  > Another point that should be revised further is around 
    clarifying the contributions of this paper. The response 
    document summarizes nicely that, together with additional 
    QBF encoding, "this paper brings together all the results 
    with extended experiments and more detailed expositions for 
    the benefit of both biological and computation community." 
    However, I did not find a similar concise statement of the 
    contributions in the text. In addition, some of the stated 
    advances over previous approaches seem incremental and minor. 
    For example, for the previous CBMC-based method it is stated 
    that "...the scalability of the method was insufficient. 
    The tool was able to handle the system with just eight 
    compartments". Yet, we learn that "A typical eukaryotic 
    cell contains 9 organelles" and even one of the methods 
    presented in this paper fails for some of the experimental 
    evaluations with 7 or more compartments. The contributions 
    of this work, perhaps in the integration and evaluation of
    several methods reported previously, should be stated clearly 
    and accurately in the main text.

  Authors response: We clarified the concerns of the reviewers 
  and clearly stated in the Sec 1. Introduction that the CBMC 
  method does not scale and the direct encoding does. 
  We have also stated that the key purpose of this paper is 
  one unified exposition of our work.

### 2019-09-16 papers/journal/2019_ACTA_Rebuttal_Rd2.txt

  Pt #1b:
-------- Mukund [Subpoint added]--------------
  > Finally, it is not clear why the goal is to find the minimum graph 
    connectivity, given that larger connectivity corresponds to a 
    more robust network. I was expecting an approach involving 
    incrementing k to find the smallest value that makes the formula 
    unsatisfiable, thus identifying the maximum graph connectedness 
    possible for a given VTS with all other constraints being 
    satisfied. However, to the best of my understanding, this is not 
    what the paper is currently proposing, or else further  
    clarifications are needed.

  Authors response: ...

  > I also found the formulation of the main problems with respect 
    to connectedness somewhat confusing. For example, in Sec. 5.1.1 
    and Sec. 5.1.2 the problems are formulated as a search for VTS G 
    such that G is not k-connected. Yet, Sec. 5.1 specifies that 
    "In case the formula is satisfiable the procedure terminates and 
    we report the value of k", which seems contradictory.

  Authors response: In Sec. 5 we try to give a high-level 
  explanation of the procedure, followed by a formal search statement 
  from the prespective of an efficient implementation. 
  This difference was only hinted but not explicitely stated. We have 
  now rewritten the parts of the text to address the distinction 
  between high-level overview and the implementation. 
  We have also removed the specific search problems (as suggested by 
  Reviewer #3 in the first revision) for further apparent accessibility 
  of the subject matter.

### 2019-09-16 papers/journal/problem.tex
Univ cond update

\subsection{Search for universal condition}
%
% Similarly, for the conjecture that k-connectedness is a universal condition for the VTS,
For some $k>0$,
we have to ensure that every graph of $k$-connected structure satisfies all
the rules of the system.
%
We also aim to find the minimum $k$. 
% We also have to ensure that the particular k is the least one. 
%
This condition can be specified as: for every $k$-connected graph, there exists a satisfiable assignment following the rules of the system. 
%
% \begin{align*}
%   & \forall G \, \texttt{Connectivity(k)} \implies  \exists
%                         f,p: \texttt{Stability} \, \land \, \texttt{Fusion}  
%   \tag{U}\label{eq:univcond}
% \end{align*}
%
We will use the same procedure as the existential condition to ensure that $k$ is minimized.
%
The formula for the problem has quantifier alternation. 
%
Most SAT solvers can check (at least efficiently) only quantifier-free formulas.
%
We need a QBF solver for such queries.
%

>>>>

\subsection{Search for universal condition}
%
% Similarly, for the conjecture that k-connectedness is a universal condition for the VTS,
For some $k>0$,
we have to ensure that every graph of $k$-connected structure satisfies all
the rules of the system.
%
We also aim to find the minimum $k$. 
% We also have to ensure that the particular k is the least one. 
%
This condition can be specified as: for every $k$-connected graph, there exists a satisfiable assignment following the rules of the system. 
%
% \begin{align*}
%   & \forall G \, \texttt{Connectivity(k)} \implies  \exists
%                         f,p: \texttt{Stability} \, \land \, \texttt{Fusion}  
%   \tag{U}\label{eq:univcond}
% \end{align*}
%
We will use the same procedure as the existential condition to ensure that $k$ is minimized.
%

For the implementation purpose, to conclude that a given $k$-connectedness is not a universal condition it is suffice to search for a $k$-connected graph that has no satisfying assignment of all the rules of the system (checking the negation of the condition is unsatisfiable).

The formula for the problem has quantifier alternation. 
%
Most SAT solvers can check (at least efficiently) only quantifier-free formulas.
%
%
We need a QBF solver for such queries. 
%
We refer the corresponding search problem as $\fqbf$ search problem.
%
